Inferring the distribution and rate of Earth-like exoplanets \\ from noisy individual-planet inferences

### 2014-03-25 document/ms.tex
discussion start

\newcommand{\nyu}{2}
\newcommand{\mpia}{3}
\newcommand{\princeton}{4}
\author{%
    Daniel~Foreman-Mackey\altaffilmark{1,\nyu},
    David~W.~Hogg\altaffilmark{\nyu,\mpia},
    Timothy~D.~Morton\altaffilmark{\princeton},
    \etal
}
\altaffiltext{1}            {To whom correspondence should be addressed:
                             \url{danfm@nyu.edu}}
\altaffiltext{\nyu}         {Center for Cosmology and Particle Physics,
                             Department of Physics, New York University,
                             4 Washington Place, New York, NY, 10003, USA}
\altaffiltext{\mpia}        {Max-Planck-Institut f\"ur Astronomie,
                             K\"onigstuhl 17, D-69117 Heidelberg, Germany}
\altaffiltext{\princeton}   {Department of Astrophysics, Princeton University,
                             Princeton, NJ}

@@

This study is novel in a number of ways.
We create probabilistic information about the full exoplanet population
  \emph{not} by weighting the detected objects by the inverse detection efficiency (CITE PETIGURA),
  but rather by forward modeling the observed distribution subject to the detection efficienty.
Re-weighting the data by inverse selection probability---%
  a method called V-max in the quasar and galaxy luminosity function contexts---%
  is not wrong,
  but it produces a higher-variance estimate of the population than a justified likelihood approach.
Here our likelihood function is a Poisson rate likelihood;
  it makes the fundamental assumption that the data points are independently drawn from the model,
  but no other assumptions.
Indeed, the assumptions behind this study are weaker than those of any previous study
  of the Earth-analog population (CITE PETIGURA, DONG).

@@

>>>>

\newcommand{\nyu}{2}
\newcommand{\mpia}{3}
\newcommand{\princeton}{4}
\author{%
    Daniel~Foreman-Mackey\altaffilmark{1,\nyu},
    David~W.~Hogg\altaffilmark{\nyu,\mpia},
    Timothy~D.~Morton\altaffilmark{\princeton},
    \etal
}
\altaffiltext{1}            {To whom correspondence should be addressed:
                             \url{danfm@nyu.edu}}
\altaffiltext{\nyu}         {Center for Cosmology and Particle Physics,
                             Department of Physics, New York University,
                             4 Washington Place, New York, NY, 10003, USA}
\altaffiltext{\mpia}        {Max-Planck-Institut f\"ur Astronomie,
                             K\"onigstuhl 17, D-69117 Heidelberg, Germany}
\altaffiltext{\princeton}   {Department of Astrophysics, Princeton University,
                             Princeton, NJ, 08540, USA} % CHECK THIS ZIP CODE

@@

This study is novel in a number of ways.
We create probabilistic information about the full exoplanet population
  \emph{not} by weighting the detected objects by the inverse detection efficiency (CITE PETIGURA),
  but rather by forward modeling the observed distribution subject to the detection efficienty.
Re-weighting the data by inverse selection probability---%
  a method called V-max in the quasar and galaxy luminosity function contexts---%
  is not wrong,
  but it produces a higher-variance estimate of the population than a justified likelihood approach.
One simple intuition along these lines is that the inverse probability weights can be large in dynamic range,
  so the effective number of samples, after weighting, can be much smaller than the actual number of samples.
Another is that it tends to upweight most strongly the most marginal detections in the data sample,
  since these tend to be the samples that lie in the region of lowest completeness.
In this work, we build a justified likelihood of the observed data,
  taking into account the completeness function or detection efficiency.
Our likelihood function is a variable-rate Poisson likelihood;
  it makes the fundamental assumption that the data points are independently drawn from the model,
  but is agnostic about all other properties of the data or distribution functions.
Indeed, the assumptions behind this study are weaker than those of any previous study
  of the Earth-analog population (CITE PETIGURA, DONG).

@@

\section{Results}

\section{Discussion}

We have made the first measurement of the Earth-like exoplanet population
  that is based on forward modeling,
  takes proper account of the observational uncertainties on planet radii,
  and makes use of extremely flexible non-separable distributions for radius and period.
We find BLAH BLAH BLAH.

Although our method makes weaker assumptions than any previous work in this area,
  of course it \emph{does} make strong assumptions.
It assumes that the data set (provided by CITE PETIGURA)
  contains planets and only planets (no false positives).
It assumes that the individual-planet radius uncertainties
  are also correctly determined.
It assumes that the completeness calculation (CITE PETIGURA)
  is accurate and smoothly varying with radius and period;
  it makes no attempt to adjust the completeness star-by-star for brightness or variability.
It assumes that the exoplanets are all independently drawn from the same distribution function,
  with no regard to age, metallicity, or multiplicity.

Although we have taken account of the radius uncertainties in a principled way,
  we did make one important approximation:
We ignored planets with central values far outside the radius and period box in which we built the model.
That is, we assumed that there are no very large outliers in radius determination.
This assumption is a complex one;
  it involves the effective, end-to-end error distribution in the data set,
  but also smoothness of the distribution function at or near the edges of the analysis box.

If our inferences are right about true Earth analogs,
  then we expect that there are about XXX transiting Earth analogs
  hidden in the \kepler\ data set.
We would be able to find some of these Earth analogs if the effective noise level in the data could be reduced
  by a factor of about XXX.
We have identified a number of directions along which this noise reduction might happen,
  including but not limited to
  retrospective data-driven or physics-driven recalibrations of the \kepler\ focal plane (CITE HOGG WHITEPAPER),
  new methods for performing aperture photometry (NOTHING TO CITE),
  and better models for stochastic stellar variability that take account of frequency structure (CITE CARTER, BREWER, AIGRAIN).
If any (or all) of these deliver substantial improvements for \kepler\ archival data reanalyses,
  it's Nobel Prize time!  (Or at least \textsl{The Colbert Report}?)
